---
title: "Final Report: Are Th17 cells or neutrophils associated with rapid PKD?"
date: 2026-07-24
author: "Morgan Yashchenko"
---

# Are Th17 cells or neutrophils associated with rapid PKD?

## Introduction

Consensus in the Polycystic Kidney Disease (PKD) field is that kidney injury accelerates cystic kidney disease in mice. This phenomenon has never been definitively shown in humans, but it is assumed to be the same, therefore immense caution is taken to try and prevent injury in human PKD kidneys.

With any tissue injury comes inflammation. This is characterized by infiltration of immune cells, production of inflammatory cytokines, and clearing of dead/defective host cells.

Our lab believes it is this inflammation that is causing acceleration of cyst growth. We found that interferon gamma was highly elevated in rapidly progressing-injured cystic mice compared to slowly progressing. When we knocked out interferon gamma, it significantly slowed disease progression after injury.

Interestingly, neutrophils and Th17 cells were substantially diminished with the loss of interferon gamma. Could these cell types be responsible for the injury acceleration phenotype?

Let's do some EDA to see if there is anything that sticks out.

## Methods

We performed flow cytometry, serum blood urea nitrogen (BUN) assay, H&E and PicroSirius histology for cystic analysis and fibrosis measurements on the following groups:

- injured cystic mice
- injured cystic mice with interferon gamma KO

Our controls groups were:

- injured noncystic mice
- injured noncystic mice with interferon gamma KO
- non-injured cystic mice
- non-injured cystic mice with interferon gamma KO

## Results

Share your findings here. You can include:

- Text explanations
- Tables
- Figures and visualizations
- Code examples (if relevant)

### Example Code Block

First, here are the packages used for this analysis:

```{r}
# Load a library
library(ggplot2)
library(tidyverse)
library(tidymodels)

# Create some sample data
data <- data.frame(
  x = 1:10,
  y = rnorm(10)
)

# Make a plot
plot(data$x, data$y)
```


Now, lets look at the data. What groups do we have?
```{r}
#

```
There are a lot of comparisons we can make, but let's choose the most relevant to our question. We first want to ask:

Do Th17 cell numbers correlate with disease parameters? (grid)

So lets compare Th17 cell values per sample with:

KW/BW?
Cystic index?
fibrosis?
BUN?

Do neutrophil numbers correlate with disease parameters? (grid)
KW/BW?
Cystic index?
Fibrosis?
BUN?


What about in our non-injured, rapidly-progressing model?
Th17 and neutrophil correllations of parameters

heatmap?




### Example Table

| Method | Result | P-value |
|--------|--------|---------|
| Analysis 1 | Significant | 0.01 |
| Analysis 2 | Not Significant | 0.15 |

## Discussion

What do your results mean? How do they relate to your research question? What limitations exist? What would you do next?

## Conclusions

Summarize your findings and their implications.

## References

Add any references to papers, data sources, or resources you used.

---

**Last updated:** July 2026
